Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Mention exponential slowdown after Hopcroft-Ullman definition.

>>>>

Therefore,
using Hopcroft and Ullman's definition,
we could enumerate functions that are not computable;
so, the image of the corresponding ``Gödel numbering''
would include not only computable functions.

A tentative fix to this definition is to force all branches to halt;
but now, as all branches are required to return the same value,
the machine is almost deterministic.
Therefore, if there is a machine $M$ that computes the characteristic function%
\footnote{
    The characteristic function of a set $A \subseteq \Sigma^*$
    is the function $f$ defined by
    \begin{equation*}
        f(x) = \begin{cases}
            1, & \text{if $x \in A$}. \\
            0, & \text{if $x \notin A$}.
        \end{cases}
    \end{equation*}
}
of the satisfiability problem in nondeterministic polynomial time,
we could simulate $M$ on a given input,
choosing (say) always the first option when confronted with nondeterminism.
If this branch of computation returns $1$,
then every branch returns $1$ and the input is satisfiable;
if this branch returns $0$, every branch returns $0$ and the input is unsatisfiable.
We thus could solve $\SAT$ in \emph{deterministic} polynomial time.

Therefore, with this restriction,
we lose the apparent exponential speed up in computation time%
\footnote{
    It is ``apparent'' in the sense that,
    if $\P \neq \NP$,
    we will have this exponential slowdown in some problems
    when moving from nondeterministic to deterministic machines.
}
we have when using nondeterminism.
The following definitions we will see
does not suffer from this problem.
